\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter

%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{\uppercase{#1}}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill}  \location{#3 | #4}\\
\descript{#2}\fakeNewLine}

% Create project heading. Parameters: Name, link, Tech stack
\newcommand{\projectHeading}[3]{\Project{#1}{#2}
\descript{#3}\\}

\newcommand{\projectHeadingWithDate}[4]{\Project{#1}{#2}
\descript{#3 | #4}\\}

% Parameters: courses
\newcommand{\courseWork}[1]{\textbf{Coursework:} #1}

% Parameters: courses
\newcommand{\teacherAssistant}[1]{\textbf{Teacher Assistant (TA):} #1}
 
%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{Rinika Dey}
% How you want it to show up on the resume
\newcommand{\yourWebsite}{www.google.co.in}
% vs how you want it to show up. If it's the same you can just replace "\yourWebsiteLink" with "yourWebsite"
\newcommand{\yourWebsiteLink}{https://www.google.co.in/}
\newcommand{\yourEmail}{pori75dey@gmail.com}
\newcommand{\yourPhone}{+917890680872}
\newcommand{\githubUserName}{RinikaDey}
\newcommand{\linkedInUserName}{rinikadey}

% An alternate profile section 
% \alignProfileTable
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%     \ralewayBold{\href{\yourWebsiteLink}{\Large \yourName}} & 
%     Email : \href{mailto:\yourEmail}{\yourEmail}
%     \\
%     \href{https://github.com/\githubUserName}{GitHub://\githubUserName} & 
%     Mobile : \yourPhone
%     \\
%     \href{https://www.linkedin.com/in/\linkedInUserName}{LinkedIn://\linkedInUserName} & Website : \href{\yourWebsiteLink}{\yourWebsite}
%     \\
% \end{tabular*}

\begin{center}
    \Huge \scshape \latoRegular{\yourName} \\ \vspace{1pt}
    \small \href{mailto:\yourEmail}{\underline{\yourEmail}}  $|$  \yourPhone $|$ 
    \href{https://www.linkedin.com/in/\linkedInUserName}{\underline{linkedIn/\linkedInUserName}} $|$
    \href{https://github.com/\githubUserName}{\underline{github/\githubUserName}} 
    % $|$ \href{\yourWebsiteLink}{\underline{\yourWebsite}}
\end{center}

%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{Education}
\educationHeading{MCA}{Maulana Abul Kalam Azad University of Technology (MAKAUT)}{Regent Education and Research Foundation  Group of Institutions, (9.71 of 10)}{2019 - 2022}

%\teacherAssistant{World Wide Web Information Systems Development}
%\courseWork{DSA; OOP with Java; DBMS I; DBMS II; C; C++; Software Engineering and TQM; Computer Networks; Business Management; Unix and Shell Programming}
\sectionsep

% Put school first and degree second if your school is reputable
\educationHeading{BSc. (Major) Computer Application}{West Bengal State University (WBSU)}{Rishi Bankim Chandra College, (64.13 of 100)}{2015 - 2018}

%\teacherAssistant{World Wide Web Information Systems Development}
%\courseWork{C; C++; DBMS; CN; Shell, Microprocessor, Computer Organization and Architecture}
\sectionsep

%--------------------------------------------------------------
%     Experience
%--------------------------------------------------------------
\section{Experience}
\resumeHeading{Symmetrix Systems Pvt Ltd}{Web Developer Trainee}{Kolkata, ON}{Oct 2023 - May 2024}
\begin{bullets}
    \item Developed \textbf{custom WordPress themes} tailored to client needs. 
    \item Worked on \textbf{core PHP} applications.
    \item Managed and customized \textbf{WordPress CMS} for improved functionality.
    \item Implemented \textbf{SEO strategies} to boost website \textbf{performance}.
    \item Worked on some \textbf{HTML/CSS} frontend designs.
\end{bullets}
\sectionsep

\resumeHeading{Codearts Solution Pvt Ltd}{Jr. Web Developer Intern}{Kolkata, ON}{Aug 2022 – April 2023}
\begin{bullets}
    \item Developed multiple components of ERM, an internal product of Codearts Solution Pvt. Ltd. like \textbf{Holiday Module, Notice Module, Chat Module} etc. in \textbf{PHP, MYSQL, HTML, CSS, JS, JQUERY, BOOTSTRAP} both frontend and backend with \textbf{AJAX calls and PHP SESSIONS} maintaining PR on daily basis using \textbf{GIT and GITHUB}. 
    \item Worked on \textbf{Wordpress Theme Development, Content Management, Wocommerce} etc. helping multiple clients like \textbf{KMG Import, IRON CURTAIN CUSTOMS, Hair Doctor NYC} etc.
\end{bullets}
\sectionsep

\resumeHeading{Shunya Intelliware Solutions}{Trainee Software Developer Intern}{Kolkata, ON}{May 2022 –  Jul 2022}
\begin{bullets}
    \item Observed \textbf{design} of various websites, making \textbf{detailed reports} of these websites.
    \item Testing various cases for \textbf{android apps and websites}.
\end{bullets}
\sectionsep


%--------------------------------------------------------------
%     Projects
%--------------------------------------------------------------
\section{Projects}
  
\projectHeading{Codearts ERM}{https://github.com/RinikaDey/codearts-ERM}{Html, Css, Javascript, Bootstrap, PHP, Mysql}
A Employee Management System i.e. ERM for managing all modules like, employee profile, leave, holiday, timesheet, gracetime, notice, access log etc.\\
\sectionsep

\projectHeading{KMG-Import}{https://www.kmg-import.com/}{Wordpress, Woocommerce, Html, Css, Javascript, Bootstrap, PHP}
A live eCommerce website built with woocommerce.\\
\sectionsep

\projectHeading{Wordpress Website with Custom theme, Backend and Database}{https://github.com/RinikaDey/wordpress_database}{Wordpress, Theme Development, PHP, Mysql, Html, Css, Bootstrap}
A custom theme for wordpress.\\
\sectionsep

\section{Other Projects}

\projectHeading{Worked on}{https://www.linkedin.com/in/rinikadey/}{}
Website design checking, Android app testing, Laravel framework, Artificial Intelligence, Neural Network
\sectionsep

  

%--------------------------------------------------------------
%     Skills
%--------------------------------------------------------------
\section{Skills}
\begin{skillList}
    \singleItem{Languages:}{Java, C, C++, PHP, SQL, Python}
    \\
    \singleItem{Web Development:}{PHP, JavaScript, Wordpress, HTML, CSS, Bootstrap}
    \\
    \singleItem{Technology:}{Git, Github, Postman, Linux, XAMP stack}
    \\
    \singleItem{Achievement:}{Employee of the month (November'2022) \textit{(Associated with \textbf{Codearts Solution Pvt Ltd})}}
\end{skillList}

\end{document}